---
title: 'BAY2416964-AHR 20201 Expansion\n :: ASCO Figures'
author: "Martin Szyska <martin.szyska@bayer.com>"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    dev: svg
    df_print: paged
    highlight: haddock
    code_folding: hide
    html_notebook: null
    theme: journal
    toc: yes
    toc_depth: 3
    toc_float: yes
study: 20201-BAY2416964-AHR (s3://kumo-20201-bay2416964-ahr/20201_AhR_RNAseq/)
---

```{r include=FALSE, cache=T}
{
    ##################################
    ## SETUP #########################

    # Load the helper repo
    hook <- file.path(Sys.getenv('HOME'), "Sites/projectsceleton/code/R")
    source(file.path(hook,"setup.R"))

    config_setup <- file.path(Sys.getenv('WORK'), "Projects/AhR/AhRKumo/Programs/config/AhR_setup.yml")
    run_setup(config_setup)
    ## --> functions and variables are loaded


    ####### SET THE PLOTTING CONFIG
    config_file <- file.path(config_path, "AhReport.yml")
    #########################################################################################
    #################### SET PLOTTING FUNCTIONS #############################################
    ### MetaData is already prepared by pandas workflow
    
    options(DT.options = list(pageLength = 30))
    plot_patient_info <- use_with_config(plot_table, config_file)
    plot_sites1 <- use_with_config(plot_sites, config_file)
    plot_AllSig <- use_with_config(plot_signatureAll, config_file)
    plot_PatientSig <- use_with_config(plot_signature, config_file=config_file)
    plot_PatientBox <- use_with_config(plotBox, config_file=config_file)
    plotXY <- use_with_config(plot_xy, config_file=config_file)
    plotXYside <- use_with_config(plot_xy_side, config_file=config_file)
}

###################### GET THE DATA #####################################################
#########################################################################################
{
    ###################################################
    # LOAD THE ALMAC TPM data and merge together
    ####### GENE DATA ################
    if (!load_data()) {
        dataMS <- use_with_config(load_ALMAC_TPM, config_file)()
        dataMS <- use_with_config(get_all_signatures, config_file)(data=dataMS)
        message(str_glue("Saving data to {RData_path}"))
        save(dataMS, file = RData_path)
    }

    # geneInfoMS <- dataMS[["geneInfo"]]
}
```
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# Signature plots {.tabset .tabset-pills}

## Merck 18 gene signature {.tabset .tabset-pills}
For this signature, I have a few graphical options you can choose from - just pick one combination of color, point size and I will use this for the other figures as well

### Labels
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=10, fig.height=8}
plot_PatientBox(dataMS,
    ycol="Merck_18Gene_IFNy"
        )
```

### noLabels
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=10, fig.height=8}
plot_PatientBox(dataMS,
    ycol="Merck_18Gene_IFNy",
    pointLabel=""
        )
```


## David CD4|CD8 signature {.tabset .tabset-pills}

This is the signature you were proposing during the brainstorm. 
It contains:
    + CD3E
    + CD3D
    + CD3G
    + CD2
    + CD8A
    + CD8B
    + GZMB
    + PRF1

### Labels
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=10, fig.height=8}
plot_PatientBox(dataMS,
    ycol="David_CD4CD8",
    pointColor="AhR_Nuclear23",
    pointLabel="AhR_Nuclear23"
)
```

### noLabels
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=10, fig.height=8}
plot_PatientBox(dataMS,
    ycol="David_CD4CD8",
    pointColor="AhR_Nuclear23",
    pointLabel=""
)
```

# Correlations Merck with NuclearAhR 2+3 {.tabset .tabset-pills}
Correlations are not visible - I only used the SCR samples of the expansion cohort

## IFNy vs Nuclear23 {.tabset .tabset-pills}

### with Labels
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=12, fig.height=10}
(plot_correl1 <- plotXY(data=dataMS,
    filters=list(
        PVC="SCR",
        CancerType="LungCancer"
    ),
    xcol="AhR_Nuclear23",
    xLabel="AhR Nuclear2+3",
    ycol="Merck_18Gene_IFNy",
    yLabel="Merck 18gene-IFNy Signature Score",
    pointLabel="AhR_Nuclear23",
    pointColor="AhR_Nuclear23"
    ))
```

### no Labels
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=12, fig.height=10}
(plot_correl1 <- plotXY(data=dataMS,
    filters=list(
        PVC="SCR",
        CancerType="LungCancer"
    ),
    xcol="AhR_Nuclear23",
    xLabel="AhR Nuclear2+3",
    ycol="Merck_18Gene_IFNy",
    yLabel="Merck 18gene-IFNy Signature Score",
    pointLabel="",
    pointColor="AhR_Nuclear23"
    ))
```

### with linReg
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=12, fig.height=10}
(plot_correl1 <- plotXY(data=dataMS,
    filters=list(
        PVC="SCR",
        CancerType="LungCancer"
    ),
    xcol="AhR_Nuclear23",
    xLabel="AhR Nuclear2+3",
    ycol="Merck_18Gene_IFNy",
    yLabel="Merck 18gene-IFNy Signature Score",
    pointLabel="",
    pointColor="AhR_Nuclear23",
    linRegress=T,
    linRegSE=F
    ))
```

### with linReg + SE
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=12, fig.height=10}
(plot_correl1 <- plotXY(data=dataMS,
    filters=list(
        PVC="SCR",
        CancerType="LungCancer"
    ),
    xcol="AhR_Nuclear23",
    xLabel="AhR Nuclear2+3",
    ycol="Merck_18Gene_IFNy",
    yLabel="Merck 18gene-IFNy Signature Score",
    pointLabel="",
    pointColor="AhR_Nuclear23",
    linRegress=T,
    linCorrEff=5
    ))
```

## CD4+CD8 vs Nuclear23 {.tabset .tabset-pills}

### with Labels
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=12, fig.height=10}
(plot_correl1 <- plotXY(data=dataMS,
    filters=list(
        PVC="SCR",
        CancerType="LungCancer"
    ),
    xcol="AhR_Nuclear23",
    xLabel="AhR Nuclear2+3",
    ycol="David_CD4CD8",
    yLabel="CD4|CD8 Signature Score",
    pointLabel="AhR_Nuclear23",
    pointColor="AhR_Nuclear23"
    ))
```

### no Labels
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=12, fig.height=10}
(plot_correl1 <- plotXY(data=dataMS,
    filters=list(
        PVC="SCR",
        CancerType="LungCancer"
    ),
    xcol="AhR_Nuclear23",
    xLabel="AhR Nuclear2+3",
    ycol="David_CD4CD8",
    yLabel="CD4|CD8 Signature Score",
    pointLabel="",
    pointColor="AhR_Nuclear23"
    ))
```

### with linReg
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=12, fig.height=10}
(plot_correl1 <- plotXY(data=dataMS,
    filters=list(
        PVC="SCR",
        CancerType="LungCancer"
    ),
    xcol="AhR_Nuclear23",
    xLabel="AhR Nuclear2+3",
    ycol="David_CD4CD8",
    yLabel="CD4|CD8 Signature Score",
    pointLabel="",
    pointColor="AhR_Nuclear23",
    linRegress=T,
    linRegSE=F
    ))
```

### with linReg + SE
```{r echo=FALSE, message=FALSE, result=FALSE, fig.width=12, fig.height=10}
(plot_correl1 <- plotXY(data=dataMS,
    filters=list(
        PVC="SCR",
        CancerType="LungCancer"
    ),
    xcol="AhR_Nuclear23",
    xLabel="AhR Nuclear2+3",
    ycol="David_CD4CD8",
    yLabel="CD4|CD8 Signature Score",
    pointLabel="",
    pointColor="AhR_Nuclear23",
    linRegress=T,
    linCorrEff=5
    ))
```
